Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-09 GWLDCII.tex
a few comments on comments

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but \st{this is different to what occured in $I_{n-2}^{V}$}{\color{violet}but some other propagator must contribute $n-1$ to $I_{n-2}^{V}$} so we cannot use the same argument as above. When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\begin{lem}\label{lem n and n-1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}.
Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
\end{lem}

@@

  \begin{figure}
    \[\includegraphics{messy}\]
    \caption{Plusses coming from $I_{n-2}^{V}$ (top left), $I_{n-1}^{V}$ (top right), and $I_n^V$ (bottom row), in the case where ${n-1, n-2\in I_{n-2}^{V}}$.  The blue lines are the non-intersecting paths defining the position of the plusses.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure} \sanote{can we put the diagrams labels in bold or set them apart somehow so that it is easier to see? Esp since they are located in a different part of the diagram for $I_n^V$?}

>>>>

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but \st{this is different to what occured in $I_{n-2}^{V}$}{\color{violet}but some other propagator must contribute $n-1$ to $I_{n-2}^{V}$} so we cannot use the same argument as above. When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}\note{The point is, at $n-2$ $q$ must contribute $n-2$ (because nothing else is supported on $n-2$), and so by the intervals being cyclic, nonempty, and never getting the last vertex, at $n-1$ (and identically at $n$ since $n-1$ doesn't support anything) $q$ contributes $n-5$.}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\begin{lem}\label{lem n and n-1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}.
Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?}\note{I don't remember, but the point is that this is a two way statement, $I_n^W$ nd $I_{n-1}^W$ yield \emph{exacly} the plusses yielded by $I_n^{V}$, and it doesn't really matter which come from $I_n^W$ and which from $I_{n-1}^W$} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
\end{lem}

@@

  \begin{figure}
    \[\includegraphics{messy}\]
    \caption{Plusses coming from $I_{n-2}^{V}$ (top left), $I_{n-1}^{V}$ (top right), and $I_n^V$ (bottom row), in the case where ${n-1, n-2\in I_{n-2}^{V}}$.  The blue lines are the non-intersecting paths defining the position of the plusses.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure} \sanote{can we put the diagrams labels in bold or set them apart somehow so that it is easier to see? Esp since they are located in a different part of the diagram for $I_n^V$?}\note{That's going to come down to journal style in the end, so only do it if it is easy and you know how to do it by an appropriate option}
